---
title: "De-duplication"
author: "Amenze Okpah"
date: "June 28, 2018"
output: html_document
---

compare similarity between two numeric vectors using Symbolic Aggregate approXimation (SAX).
Symbolic Aggregate approXimation (SAX) algorithm application to the input time series transforms its into a strings.
The algoithm was proposed by Lin et al.) and extends the PAA-based approach inheriting the original algorithm simplicity and low computational complexity while providing satisfactory sensitivity and selectivity in range query processing. Moreover, the use of a symbolic representation opened a door to the existing wealth of data-structures and string-manipulation algorithms in computer science such as hashing, regular expression, pattern matching, suffix trees, and grammatical inference.
#http://www.cs.ucr.edu/~eamonn/SAX.htm
#https://jmotif.github.io/sax-vsm_site/morea/algorithm/PAA.html

```{r}
# create a list from these files
dir <- choose.dir(default = "", caption = "Select folder")
list.filenames<-list.files(dir,pattern=".csv$")
#extract files based on duplicated utctime
for (i in 1:length(list.filenames))
{
  patient<-read.csv(list.filenames[i])
  patient_cbg<-subset(patient,patient$type=="cbg")
  if ((length(unique(patient_cbg$utcTime)))!=nrow(patient_cbg))
      write.csv(patient_cbg,paste0(dir,list.filenames[i]))
 }
```
  # Coverts two vectors to their string equivalent
  # Args:
  # x:vector of numeric values for uploadid1 
  # y:vector of numeric values for uploadid2 
  # alpha.Size: alphabet size(number of character that will be used to discretized numeric values)
  # Returns:
  #   longeststring:longest common substring match between discretized valuea of x and y respectively stringX,stringY
  # percentage similarity between vector x and y

#Note: since PAA takes normalized values,vectors are normalized using the mean and standard deviation of either vector (x or y)
#PAA:the length of PAA values are fixed to length of the vectors to avoid reducing the dimensions since all values are needed to check for duplication.
```{r}
StringConvert <- function(x, y, alpha.Size){
  if (length(x) != length(y)){
    normvalue = x
  }
  else if(length(x) == length(y)){
    normvalue = x
  }
  normvalue.Mean <- mean(normvalue)
  normvalue.Dev <- sd(normvalue)
  xnormalized <- (x - normvalue.Mean) / normvalue.Dev
  ynormalized <- (y - normvalue.Mean) / normvalue.Dev
  X.PAA = paa(xnormalized, length(x)) 
  y.PAA = paa(ynormalized,  length(y))
  xString.Value <- series_to_string(X.PAA, alpha.Size)
  yString.Value <- series_to_string(y.PAA, alpha.Size) 
  stringX <- xString.Value
  stringY <- yString.Value
  longeststring<-LCSn(c(stringX,stringY))
  return (list(longeststring, stringX, stringY, (levenshteinSim(xString.Value, yString.Value))))
}
```
#computes the range of matching character between string values and common subsequence
  Args:
    values:output from stringcnvert function 
  Returns:
     Loc:Matching Ranges
```{r}
IndexRange<-function(values){
  strings.Values <- as.character(c(values[2],values[3]))
  common.SubSequence <- as.character(values[1])
  loc <- str_locate(strings.Values, common.SubSequence)
  return(list(loc))
}
```
##computes the duplicated values for each vectors and their indexes 
  # Args:
  # x & y: vectors
  # Returns:
  #   duplicated.X:duplicated value for vextor x
  # duplicated.Y:duplicated value for vextor y
  # index.X:duplicated values index for vector x
  # index.Y:duplicated values index for vector y
```{r}
ExtractDuplicateIndex <- function(x, y, IndexRange){
   duplicate.X <- x[IndexRange[[1]][1,][1] : IndexRange[[1]][1,][2], "value"]
   duplicate.Y <- y[IndexRange[[1]][2,][1] : IndexRange[[1]][2,][2], "value"]
   index.X <- row.names(x[IndexRange[[1]][1,][1] : IndexRange[[1]][1,][2],])
   index.Y <- row.names(y[IndexRange[[1]][2,][1] : IndexRange[[1]][2,][2],])
return(list(duplicate.X, duplicate.Y, index.X, index.Y))
}
```
##computes a list of indexes 
  Args:
    x: vectors
  Returns:
    duplicate.Index:duplicated value index
```{r}
ExtractVectorIndex<-function(x){
  for (i in 1:length(x))
  indexnum <- c(x[[i]]) 
  duplicate.Index<-as.numeric(indexnum)
return(duplicate.Index)
}
```
#import files and subset data based on uploadIds to test  function

```{r}
##read in file and check for duplicated utcTime
field <- c("deviceId", "id", "uploadId", "utcTime", "type", "value")
patient <- read.csv("FileName ")[,field] #0289cfb8bd6d61ccf1f31c07aa146b7b14f0eb74474be4311860d9d77dd30f15.csv
patient$mgvalue <- patient$value*18.01559

#check for unique uploadIds
uniqueid <- function(df){
   for (i in df["uploadId"]){
     Id <- unique(df$utcTime)
   return (Id)
   }
}
###subset patient file based on  5 uploadids
df1 <- subset(patient, patient$uploadId == "upid_3c41703c2d3a8b97f479afdb6ccf799f")
df2 <- subset(patient, patient$uploadId == "upid_3fc32e5ad912a8ea7efced9151804bdb")
df3 <- subset(patient, patient$uploadId == "upid_17db2d2a0ae0e02a12c0a5067e5fe85b")
df4 <- subset(patient, patient$uploadId == "upid_5fad608cf32bd03a1cd56e3bb1fdb834")
df5 <- subset(patient, patient$uploadId == "upid_830c6de3e2ecbbec6fbad0cecc64bdf5")

#plot values for each uploadid
par(mfrow=c(3, 3))
plot.ts(df1$value)
plot.ts(df2$value)
plot.ts(df3$value)
plot.ts(df4$value)
plot.ts(df5$value)

```

```{r}
system.time(values <- StringConvert(df1$mgvalue, df2$mgvalue,3))  #http://www.cs.ucr.edu/~eamonn/SAX.pdf alphabet size: 5-8 works better.
system.time(strngindex <- IndexRange(values))
validate <- ExtractDuplicateIndex(df1, df2, strngindex)
seq1 <- ExtractVectorIndex(validate[3])
seq2 <- ExtractVectorIndex(validate[4])
df1_mgvalue <- patient[seq1,"value"]
df2_mgvalue <- patient[seq2,"value"]
compare <- data.frame(df1_mgvalue,df2_mgvalue)

#plot duplicated values
plot.zoo(cbind(compare$df1_mgvalue, compare$df2_mgvalue), 
         plot.type = "multiple", 
         col = c("red", "blue"))
sum(compare$df1_mgvalue - compare$df2_mgvalue)
```

```{r}
values <- StringConvert(df3$mgvalue, df4$mgvalue,3 ) #http://www.cs.ucr.edu/~eamonn/SAX.pdf alphabet size: 5-8 works better. ##3 worked better for this run
strngindex <- IndexRange(values)
validate <- ExtractDuplicateIndex(df3,df4,strngindex)
seq1 <- ExtractVectorIndex(validate[3])
seq2 <- ExtractVectorIndex(validate[4])

df1_mgvalue <- patient[seq1,"value"]
df2_mgvalue <- patient[seq2,"value"]
compare <- data.frame(df1_mgvalue, df2_mgvalue)
plot.zoo(cbind(compare$df1_mgvalue, compare$df2_mgvalue), 
         plot.type = "multiple", 
         col = c("red", "blue"))
sum(compare$df1_mgvalue - compare$df2_mgvalue)
```

```{r}
patient <- read.csv("filename")[,field] #0fe539475b52ae23f939d7dd2596cf8eb1e877edcea0478f2df73bb98bd5937c.csv
patient$mgvalue <- patient$value*18.01559
length(unique(patient$uploadId)) 
length(unique(patient$id))==nrow(patient) 
length(unique(patient$utcTime))
anyDuplicated(patient$utcTime) 
length(unique(patient$utcTime))==nrow(patient) 
df1<-subset(patient,patient$uploadId=="2f61322480c841fd8679fe81e94930b2")
df2<-subset(patient,patient$uploadId=="c05970591b404518a1cbd64595d628e5")
```

```{r}
values <- StringConvert(df1$mgvalue,df2$mgvalue,3)
strngindex <- IndexRange(values)
validate <- ExtractDuplicateIndex(df1,df2,strngindex)
seq1 <- ExtractVectorIndex(validate[3])
seq2 <- ExtractVectorIndex(validate[4])

df1_mgvalue<-patient[seq1,"value"]
df2_mgvalue<-patient[seq2,"value"]
compare<-data.frame(df1_mgvalue,df2_mgvalue)

plot.zoo(cbind(compare$df1_mgvalue,compare$df2_mgvalue), 
         plot.type = "multiple", 
         col = c("red", "blue"))
sum(compare$df1_mgvalue-compare$df2_mgvalue)

```
